---
title: "607 HW 3"
author: "simplymathematics"
date: "September 16, 2018"
output: html_document
---

This code creates a data frame from the raw data.
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

library(stringr)

names <- unlist(str_extract_all(raw.data, "[a-zA-Z]+[,]*[.]*[\\ ]+[a-zA-Z]+[.\\ ]*[a-zA-Z]*"))

phones <- unlist(str_extract_all(raw.data, "[(]*[\\d{3}]*[) ]*[\\d]{3}[-\\ ]*[\\d]{4}"))

df<-data.frame(name=names, phone= phones)
df
```
This following code reverses the names if they contain a comma. This will break everything if a name legitimately has a comma.
```{r}
reversed.names <- str_split(names, ", ", simplify = TRUE)

names <- str_c(reversed.names[, 2], reversed.names[, 1])
names <- str_replace(names, "([a-z])([A-Z])", "\\1 \\2")
```
The following code creates 2 vectors with first names and last names respectively. Then, it creates a boolean vector denoting whether a name contains a title. It then stores these in a dataframe called 'df.'
```{r}

first.name <- unlist(str_extract(names, "^((Mr.|Mrs.|Dr.|Rev.|Hon.).)*[[:alpha:]]*[\\w\\d]+"))

last.name <- str_extract(names,"[[:alpha:]]+($|,{5,})")

title <- c(str_detect(first.name, "Mr.|Mrs.|Dr.|Rev.|Hon."))

df<-data.frame(first.name = first.name, last.name = last.name, title=title)
df
```

```{r}
# Breaks if second name and title, but fine for this dataset. 
tmp <-str_replace_all(names, "(Mr. |Mrs. |Dr. |Rev. |Hon. )","")
second.name <- c(str_detect(tmp, "[:space:]+[:alpha:]+[:space:]+"))
#second.name <- c(tmp - title)
second.name 

```
### 4

#### 1  [0-9]\\$  
This regular expression is 1 digit between 0 and 9 followed by a '\' and the end of a line.  

1\  
2\  
3\  

#### 2 \\b[a-z]{1,4}\\b  
This expression matches a 1-4 character string made up of lowercase letters surrounded by word boundaries.  

 a  
bed   
add  

#### 3 .*?\\.txt$  
This expression matches any line that ends in .txt.  

this.txt  
that.txt  
even.this.txt.or.that.txt  

#### 4 \\d{2}/\\d{2}/\\d{4}  

This expression matches any string that has 2 digits, a '/', 2 digits, another '/', and then 4 digits, like  

01/01/1900  
12/12/1212  
35/35/3553  

#### 5 <(/+?)>/+?</\\1>  

This expressions matches a '<' followed by a lazily read '/', followed by a '>', followed by one or more lazily read '/', another '<', a '/', a '\,' and a '1>'  

<//>/</\1>  
<//>/<//\1>  
</>/</\1>  

### 9

```{r}
code <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

letters <- str_split(code,"")
sort(table(letters))

# No luck with this one. I know it has something do with frequency analysis, but nothing about this table is straightforward

```
