---
title: "607 Week 13"
author: "simplymathematics"
date: "November 25, 2018"
output: html_document
---
As always, we start with our dependencies.  I used Ubuntu 18.04 and grabbed the mongodb binaries directly from the organization's repository as the Ubuntu binaries were out of date. 

```
sudo apt-key adv --keyserver hkp://keyserver.ubuntu.com:80 --recv 0C49F3730359A14518585931BC711F9BA15703C6  
echo "deb http://repo.mongodb.org/apt/ubuntu xenial/mongodb-org/3.4 multiverse" | sudo tee /etc/apt/sources.list.d/mongodb-org-3.4.list  
sudo apt-get update  
```
Then, I install mongo-db as well as some OpenSSL dependencies. This required me to make a directory at /data/db and give ownership of that directory to my user locally. Then, I had to run the server with root permissions because it opens a port.
```
sudo apt-get install -y mongodb-org  
sudo apt install libssl-dev libsasl2-dev  
sudo mkdir -p /data/db  
sudo chown username /data/db  
sudo mongod  
```
This one loads the mongo R library.
```{r}
library('mongolite')
```

I decided to use the cars dataset because it was available when I opened the notebook. Below, we can see the cars data as a data frame.
```{r cars}
summary(cars)
df <- as.data.frame(cars)
df
```
Here, I convert the dataframe into a Mongodb collection called "collection."
```{r}
collection <- mongo(collection = "df", db = "Cars")
collection$insert(df)
```
Below shows how to call a single row and what the data looks like.
```{r}
collection$iterate()$one()
```
## Advantages

- Works better with javascript as each line is already formatted as an object.
- NoSQL databases do not require declaring variables, tables, etc. 
- No Foreign IDs
- Scales with hardware instead of number of nodes
- With nested data, nosql databases use less bandwidth than a wide csv

## Disadvantages
- Longer processing times for queries
- Stranger looking code relative to dataframe model
- Distributed nosql databases are very chatty and require much overhead
- Does not scale particularly well if tables are all related horizontally and not nested