---
title: "607 Wk 7"
author: "simplymathematics"
date: "October 14, 2018"
output: html_document
---

As always, we will start with our dependendencies. The data for this can be found [on github](https://github.com/simplymathematics/607/tree/master/Homework/7). 

```{r}
library(XML, quietly= TRUE)
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
library(rjson)

```
Reading an html table is very straightforward. 
```{r}
data.file <- "data.html"
html.data <- readHTMLTable(data.file)
html.data

```
In the XML file, we must establish a node as a root node, then unnest each node below it. Finally, we store the transpose of this data as the dataframe we see below.
```{r}
data.file <- "data.xml"
xml.data <- xmlParse(data.file)
rootNode <- xmlRoot(xml.data)
xml.data <- xmlSApply(rootNode,function(x) xmlSApply(x, xmlValue))
xml.frame <- data.frame(t(xml.data),row.names=NULL)
xml.frame
```
Jsons are a bit simpler again given that this one is formatted as a list already. (As opposed to the structure we defined on the fly in an XML). Each row is an instance of the 'books' object that complies to the .js standard.
```{r}
json.data <- fromJSON(file ="data.json", simplify = TRUE )
data.frame(json.data)
```

This file can be found on github as well as rendered as an html on rpubs [here](rpubs.com/simplymathematics/web-data)