---
title: "607 Project 1"
author: "simplymathematics"
date: "September 23, 2018"
output: html_document
---

I decided to use data from Libremap.net to fulfill this assignment. It uses data collected from community-run networks around the world. The agent collects data from the radio driver in the integrated circuit which is reported to this website as a json. However, I know nothing about scraping, and I obtained this file by inspecting the page. 

I used the tidyr library to import the JSON. There are 45 rows in this document which represent 45 different measuring devices in a single map box on the page.

```{r}
require(jsonlite)

dat <- fromJSON("libremap.json", flatten = TRUE)
dat <- dat$rows
head(dat)
```
Some information was very easy to parse because it as already set up as a vector. Latitude, longitude, agent version and agent type were parsed as below. 

```{r}
lat <- c(dat$value.lat)
lon <- c(dat$value.lon)
agent.version <- c(dat$value.api_rev)
type <- c(dat$value.type)
```
However, in order for this data collection to scale and work over time, it will need to keep track of the bounding box that was measured. Since it was stored as a list, we have to flatten the data so that each direction has its own column.
```{r}
tmp <- c(dat$bbox)
nw <- lapply(tmp, '[', 1)
ne <- lapply(tmp, '[', 2)
sw <- lapply(tmp, '[', 3)
se <- lapply(tmp, '[', 4)
```
Next, we collect data about the hardware and what data it has chosen to provide. 

```{r}
agent.plugin <- c(dat$value.attributes.submitter.plugins)
agent.location <- grepl("location", agent.plugin)
agent.bmx <- grepl("bmx", agent.plugin)
agent.wireless <- grepl("wireless", agent.plugin)
agent.system <- grepl("system", agent.plugin)
model <- c(dat$value.attributes.system.model)
hostname <- c(dat$value.hostname)
community <- c(dat$value.community)
```
Finally, we store all of these things as a big vector of vectors and look at it to make sure it's going ok.
```{r}
big.one <- cbind(time, community, lat,lon,agent.version, type, nw, ne, sw, se, agent.plugin, agent.location, agent.bmx, agent.wireless, agent.system, model, hostname)
dim(big.one)
head(big.one)

```

The next section requires iterating through the nested scan data that exists for each row of the above. Because each scan datum is a list of a list, we have to repeat the above and fill out our table. Then, we can save it all as a csv. 

```{r}
links <-c(dat$value.links)
index = 2

for (index in 2:45 ){
  types <- c(dat$value.links[[index]]$type)
 
  signal <- dat$value.links[[index]]$attributes.signal
  mac.local <- dat$value.links[[index]]$attributes.local_mac
  mac.station <- dat$value.links[[index]]$attributes.station_mac
  channel <- dat$value.links[[index]]$attributes.channel
  size <- length(types)
  size

  # repeat a line from big.one for each row of this frame
  community <- matrix(rep(community[index], size))
  lat <- matrix(rep(lat[index],size))
  lon <- matrix(rep(lon[index],size))
  version <- matrix(rep(agent.version[index], size))
  plugin <- matrix(rep(agent.plugin[index],size))
  bmx <- matrix(rep(agent.bmx[index],size))
  agent.wireless <- matrix(rep(agent.wireless[index],size))
  agent.system <- matrix(rep(agent.system[index],size))
  model <- matrix(rep(model[index],size))
  hostname <- matrix(rep(hostname[index],size))
  
  #bind them all together
  data <- cbind( community, lat, lon, version, plugin, bmx, agent.wireless, agent.system, model, hostname, signal, mac.local, mac.station, channel)
  #append to csv
  write.table(data, file="dat.csv", col.names=FALSE, append=TRUE)
}

```

